
Beyond the hardware being functionally complete, the next step will be
to raise the throughput of the I/O subsystem closer to wire speed.
The extensive buffering within the traffic manager suggests a natural
widening of the stream interface servicing the DMA engine and
accelerator.
Other RTL optimizations can eliminate dead cycles in the state machines.
The traffic manager, accelerator, and DMA engine could also be situated
in a faster clock domain, ideally at \SI{125}{\mega\hertz} alongside the
MAC, rather than be constrained to the relatively slow core
frequency of \SI{50}{\mega\hertz}.
These components are already decoupled from the rest of the design
through ready/valid handshake schemes, which streamlines the task of
inserting asynchronous FIFOs and synchronizers at the crossings.

As for software, there is potential to improve the hit rate of the
accelerator by tuning the cache replacement policy with a more accurate
heavy hitters algorithm and possibly workload-aware speculation.
Fragmentation of the value cache could become an issue with a larger
dataset, which might be mitigated by more sophisticated allocation
strategies than a simple linear scan.

In the long term, viability as a commodity datacenter appliance rests
particularly on replacing fixed-function blocks with a programmable
substrate without compromising latency.
Much greater efficiency is attainable with a VLSI implementation of the
accelerator, but an appropriate degree of generalization is necessary to
justify its expense.

The memcached-specific logic for classifying requests and constructing
responses is isolated entirely within the traffic manager.
By exchanging the traffic manager for a programmable I/O co-processor,
it becomes possible to perform arbitrary packet filtering and to
support more complicated network processing, such as TCP offload.
This also permits the accelerator to handle other varieties of key-value
stores.
Futhermore, examining a broader set of latency-sensitive applications
for alternative uses of NIC-attached scratchpad memory might lead to a
more flexible design for the accelerator.
